### 2021-04-05 Chapter-2/Chapter-2.tex
Updates from Overleaf

\subsubsection{Cryptography Libraries}
The first side-channel attack of cryptography libraries can be traced back to Kocher's timing attacks~\cite{kocher1996timing} in 1996. It exploits the the simple modular exponentiation algorithm function in many algorithms (Diffie-Helloman, RSA) implementations. The function does not run in a fixed time. By measuring the time differences between the modular exponentiation algorithm computes the exponent bits (0 or 1), Kocher's attack can recover the whole secret key bit by bit. Since then, researchers start to break all kinds of cipher implementation through side-channel attacks.   Cryptography libraries usually have several implementations for symmetric ciphers.
For example, AES can have more than five different implementations (OpenSSL). Depending on the build configuration and the return value of \textsf{CPUID}, the code may execute any implementation of them. The reference implementation usually adopts T-Tables and S-Tables to speed up the computation. However, such implementations are vulnerable to side-channels and can be exploited to retrieve the whole key~\cite{bonneau2006cache}. In addition to the reference implementation, those libraries also have side channel silent versions. However, recent studies also shows those versions also have side-channel vulnerabilities caused by compiler optimizations and human mistakes~\cite{217537}. The situation is even worse for asymmetric ciphers (e.g., Diffie-Helloman, RSA, ECDSA) because those those ciphers have a lots of big number calculations. It is hard to implement those calculations completely side-channel resistant. Recent work~\cite{arnaud2013timing,yarom2017cachebleed,yarom2014flush+} has demonstrated several end-to-end attacks to recover the private keys of those ciphers.

>>>>

\subsubsection{Cryptography Libraries}
\begin{table}
    \centering
    \caption{This table shows some common vulnerable points in cryptography implementations and the corresponding protections.}
    \label{chapter2:table:crypto}

        \begin{tabular}{lll}
            \toprule
            Implementation & Common Vulnerable Point             & Mitigation \\ \midrule
            AES &  T-table and S-table lookups   & AES instructions (AES-NI) \\&&Scalar bit-slicing \\&& Preloading tables     \\
            DES & Table lookups & Scalar bit-slicing (No implmentation) \\
            RSA & CRT optimization & Verifying the consistency with the public key\\
            & Modular exponentiation& Montgomery modular multiplication\\
            & & Base blinding and exponent blinding\\
            (EC)DSA & Scalar multiplication& Constant time implementation\\
            &Modular inversion &\\
            &Modular reduction &\\
            \bottomrule
        \end{tabular}
\end{table}

The first side-channel attack of cryptography libraries can be traced back to Kocher's timing attacks~\cite{kocher1996timing} in 1996. It exploits the the simple modular exponentiation algorithm function in many algorithms (Diffie-Helloman, RSA) implementations. The function does not run in a fixed time. By measuring the time differences between the modular exponentiation algorithm computes the exponent bits (0 or 1), Kocher's attack can recover the whole secret key bit by bit. Since then, researchers start to break all kinds of cipher implementation through side-channel attacks.  Table~\ref{chapter2:table:crypto} summarizes some common vulnerable points in cryptography library implementations.  Note that Cryptography libraries usually have several implementations for some symmetric ciphers.
For example, AES can have more than five different implementations  in OpenSSL. Depending on the build configuration and the return value of \textsf{CPUID}, the code may execute any implementation of them. The reference implementation usually adopts T-Tables and S-Tables to speed up the computation. However, such implementations are vulnerable to side-channels and can be exploited to retrieve the whole key~\cite{bonneau2006cache}. In addition to the reference implementation, those libraries also have side channel silent versions. However, recent studies also shows those versions also have side-channel vulnerabilities caused by compiler optimizations and human mistakes~\cite{217537}. The situation is even worse for asymmetric ciphers (e.g., Diffie-Helloman, RSA, ECDSA) because those those ciphers have a lots of big number calculations. It is hard to implement those calculations completely side-channel resistant. Recent work~\cite{arnaud2013timing,yarom2017cachebleed,yarom2014flush+} has demonstrated several end-to-end attacks to recover the private keys of those ciphers.
